Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study in India

### 2025-07-12 manuscript.Rmd
Add figure of patients per month to manuscript

```{r patients-per-month, echo = FALSE, results = "asis", tab.cap = "Number of patients included per month per cluster."}
patients.per.month.table |>
  modify_caption("Number of patients included per month per cluster.")
```

>>>>

```{r patients-per-month-figure, echo = FALSE, results = "asis", fig.cap = "Number of patients included per cluster per month."}
knitr::include_graphics("patients-per-month.png")
```
